### 2020-06-05 discussion.tex
tweak

\rev{The failure rates of the old batch are not matched by the new
  batch nor by experience at other facilities with the same type of
  GPU components, making this an unexpected event that had
  considerable impact on operations and on availability of the
  system. On a positive but ironic note, the corrosion process in the
  failing resistors made the GPUs act as a sensitive instrument for
  obtaining long-term integrals of component heat dynamics and
  provided lessons learned. Here we dicsuss the conclusions we can
  draw from the experience on mitigation, which keeps the system
  operating at an acceptable level and possibly even restores some of
  the lost capability, and on long-term planning, which addresses such
  scenarios in future-generation supercomputers.}

>>>>

\rev{The failure rates of the old batch are not matched by the new
  batch nor by experience at other facilities with the same type of
  GPU components, making this an unexpected event that had
  considerable impact on operations and on availability of the
  system. On a positive but ironic note, the corrosion process in the
  failing resistors made the specific GPU batch act as sensitive
  instruments for obtaining cummulative trend information from
  component heat dynamics and provided lessons learned. Here we
  dicsuss the conclusions we can draw from the experience on
  mitigation, which keeps the system operating at an acceptable level
  and possibly even restores some of the lost capability, and on
  long-term planning, which addresses such scenarios in
  future-generation supercomputers.}
